PUT YOUR TITLE HERE

### 2023-03-17 paper/manuscript.Rmd
looking for cites and reading

# introduction

>>>>

# Citation slush pile

predict w/ ML @altmejd2019
prediction with humans @dreber2015; @forsell2019

econ also has replications and issues @camerer2016

RPP has been reanalysed and complained about a lot @etz2016;@gilbert2016;@patil2016

moving goal posts around replication / interpreting results @nosek2020 (also this is worth reading!)

some sort of modeling of replications @pawel2020 (worth reading!)

note to self: got to S in going through the cites of the review paper
# introduction
